\chapter{Infinite Galois theory}
\label{section-infinite-galois}

\noindent
The Galois group is given Krull topology.



\begin{lemma}\cite[\href{https://stacks.math.columbia.edu/tag/0BU2}{Lemma 0BU2}]{stacks-project}
	\label{lemma-infinite-galois-eq-limit}
	\lean{InfiniteGalois.continuousMulEquivtoLimit}
	\leanok
	Let $K/k$ be a Galois extension with Galois group $G$.
	Let $\Lambda$ be the set of finite Galois subextensions,
	i.e., $\lambda \in \Lambda$ corresponds to $K/L_\lambda/k$
	with $L_\lambda/k$ finite Galois with Galois group $G_\lambda$.
	Define a partial ordering on $\Lambda$ by the rule
	$\lambda \geq \lambda'$ if and only if
	$L_\lambda \supset L_{\lambda'}$. Then
	$G_\lambda$ is an inverse system of finite groups over $\Lambda$,
	the transition maps are surjective, and
	$$
	G = \lim_{\lambda \in \Lambda} G_\lambda
	$$
	thus profinite.
\end{lemma}

\begin{lemma}\cite[\href{https://stacks.math.columbia.edu/tag/0BMJ}{Lemma 0BMJ}]{stacks-project}
	\label{lemma-infinite-galois-profinite}
	\lean{InfiniteGalois.ProfiniteGalGrp}
	\leanok
	Let $K/k$ be a Galois extension. The Krull topology turns $\text{Gal}(E/F)$ into a profinite topological group.
\end{lemma}

\begin{lemma}\cite[\href{https://stacks.math.columbia.edu/tag/0BMK}{Lemma 0BMK}]{stacks-project}
	\label{lemma-infinite-galois-restrict-continuous}
	\lean{InfiniteGalois.restrictNormalHomContinuous}
	\leanok
	Let $L/M/K$ be a tower of fields. Assume both $L/K$ and
	$M/K$ are Galois. Then there is a canonical surjective continuous
	homomorphism $c : \text{Gal}(L/K) \to \text{Gal}(M/K)$.
\end{lemma}

\begin{lemma}[the compatibility with open compact topology, todo]\cite[\href{https://stacks.math.columbia.edu/tag/0BMJ}{Lemma 0BMJ}]{stacks-project}
	\label{lemma-infinite-galois-krull-topology}
	Let $E/F$ be a Galois extension. The Krull topology is the coarsest
	topology such that
	$$
	\text{Gal}(E/F) \times E \longrightarrow E
	$$
	is continuous when $E$ is given the discrete topology. Then
	for any topological space $X$ and map $X \to \text{Aut}(E/F)$
	such that the action $X \times E \to E$ is continuous the induced map
	$X \to \text{Gal}(E/F)$ is continuous.
	
\end{lemma}

\begin{theorem}[Fundamental theorem of infinite Galois theory]\cite[\href{https://stacks.math.columbia.edu/tag/0BML}{Theorem 0BML}]{stacks-project}
	\label{theorem-inifinite-galois-fundamental-theorem}
	\lean{InfiniteGalois.intermediateFieldEquivClosedSubgroup}
	\leanok
	Let $L/K$ be a Galois extension. Let $G = \text{Gal}(L/K)$
	be the Galois group viewed as a profinite topological group
	(Lemma \ref{lemma-galois-profinite}). Then we have $K = L^G$ and the map
	$$
	\{\text{closed subgroups of }G\}
	\longrightarrow
	\{\text{subextensions }L/M/K\},\quad
	H \longmapsto L^H
	$$
	is a bijection whose inverse maps $M$ to $\text{Gal}(L/M)$.
	The finite subextensions $M$ correspond exactly to the open
	subgroups $H \subset G$. The normal closed subgroups $H$ of $G$
	correspond exactly to subextensions $M$ Galois over $K$.
\end{theorem}

\begin{theorem} \cite[\href{https://stacks.math.columbia.edu/tag/0BML}{Theorem 0BML}]{stacks-project}
	\label{theorem-inifinite-galois-fundamental-theorem-special-case1}
	\lean{InfiniteGalois.OpeniffFinite}
	\leanok
	Let $L/K$ be a Galois extension. In the bijection given by the Fundamental theorem of infinite Galois theory,
	the finite subextensions $M$ correspond exactly to the open subgroups $H \subset G$.
\end{theorem}

\begin{theorem} \cite[\href{https://stacks.math.columbia.edu/tag/0BML}{Theorem 0BML}]{stacks-project}
	\label{theorem-inifinite-galois-fundamental-theorem-special-case2}
	\lean{InfiniteGalois.NormaliffGalois}
	\leanok
	Let $L/K$ be a Galois extension. In the bijection given by the Fundamental theorem of infinite Galois theory,
	the normal closed subgroups $H$ of $G$ correspond exactly to subextensions $M$ Galois over $K$.
\end{theorem}

\begin{lemma}\cite[\href{https://stacks.math.columbia.edu/tag/0BMM}{Lemma 0BMM}]{stacks-project}
	\label{lemma-ses-infinite-galois}
	\lean {InfiniteGalois.restrictNormalHomKer}
	\leanok
	Let $L/M/K$ be a tower of fields. Assume $L/K$ and $M/K$ are Galois.
	Then we obtain a short exact sequence
	$$
	1 \to \text{Gal}(L/M) \to \text{Gal}(L/K) \to \text{Gal}(M/K) \to 1
	$$
	of profinite topological groups.(with a reformulation)
\end{lemma}